---
title: 
author:
date: 
output: html_document
---
```{css echo=FALSE}
p {
    font-family: "Open Sans"; 
    color: #444444;
}
```
<style>
.html-widget {
    margin: auto;
}
</style>

```{r, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

#install packages 
library(sf)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(ggrepel)
library(formattable)
library(tmap)
library(extrafont)
library(mapboxapi)
font_import("C:/Users/GraceParker/Downloads/Open_Sans")

#insert data
territories <- st_read("C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/Territories/", quiet=TRUE)

#clean BIL data
targetF <- c("01","05","12","13","21","22","28","37","45","47","51","72","60","69","66","78")
targetG <- c(1,5,12,13,21,22,28,37,45,47,51,72,60,69,66,78)
targetH <- c("01","05","12","13","21","22","28","37","45","47","51")
SETerr <- dplyr::filter(territories,FIPS %in% targetF) #filter to SE and territories
SEstates <- dplyr::filter(territories,FIPS %in% targetH) #filter to SE
# SETerrData <- dplyr::filter(data,prime_award_summary_recipient_state_fips_code %in% targetG) #filter to SE and territories

#insert function/award type and population data by year
Asst2024_raw <- read.csv("C:/Users/GraceParker/Southeast Energy Efficiency Alliance Inc/Team SEEA - Documents/Research/Project_Files/2023_FederalFundingTracker/GitHubFolder/Data_01_22_2024/BILFY2~3/FY2024~3.CSV")
Con2024_raw <- read.csv("C:/Users/GraceParker/Southeast Energy Efficiency Alliance Inc/Team SEEA - Documents/Research/Project_Files/2023_FederalFundingTracker/GitHubFolder/Data_01_22_2024/BILFY2~3/FY2024~2.CSV")
Unl2024_raw <- read.csv("C:/Users/GraceParker/Southeast Energy Efficiency Alliance Inc/Team SEEA - Documents/Research/Project_Files/2023_FederalFundingTracker/GitHubFolder/Data_01_22_2024/BILFY2~3/FY2024~4.CSV")

Asst2023_raw <- read.csv("C:/Users/GraceParker/Southeast Energy Efficiency Alliance Inc/Team SEEA - Documents/Research/Project_Files/2023_FederalFundingTracker/GitHubFolder/Data_01_22_2024/BILFY2~2/FY2023~3.CSV")
Con2023_raw <- read.csv("C:/Users/GraceParker/Southeast Energy Efficiency Alliance Inc/Team SEEA - Documents/Research/Project_Files/2023_FederalFundingTracker/GitHubFolder/Data_01_22_2024/BILFY2~2/FY2023~2.CSV")
Unl2023_raw <- read.csv("C:/Users/GraceParker/Southeast Energy Efficiency Alliance Inc/Team SEEA - Documents/Research/Project_Files/2023_FederalFundingTracker/GitHubFolder/Data_01_22_2024/BILFY2~2/FY2023~4.CSV")

Asst2022_raw <- read.csv("C:/Users/GraceParker/Southeast Energy Efficiency Alliance Inc/Team SEEA - Documents/Research/Project_Files/2023_FederalFundingTracker/GitHubFolder/Data_01_22_2024/BILFY2~1/FY2022~3.CSV")
Con2022_raw <- read.csv("C:/Users/GraceParker/Southeast Energy Efficiency Alliance Inc/Team SEEA - Documents/Research/Project_Files/2023_FederalFundingTracker/GitHubFolder/Data_01_22_2024/BILFY2~1/FY2022~2.CSV")
Unl2022_raw <- read.csv("C:/Users/GraceParker/Southeast Energy Efficiency Alliance Inc/Team SEEA - Documents/Research/Project_Files/2023_FederalFundingTracker/GitHubFolder/Data_01_22_2024/BILFY2~1/FY2022~4.CSV")

#insert population data
pop2022_raw <- read.csv("C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/POP2022.csv")

#append data together
funData <- rbind(Asst2023_raw, Con2023_raw)
funData <- rbind(funData, Unl2023_raw)
funData <- rbind(funData, Asst2022_raw)
funData <- rbind(funData, Con2022_raw)
funData <- rbind(funData, Unl2022_raw)
funData <- rbind(funData, Asst2024_raw)
funData <- rbind(funData, Con2024_raw)
funData <- rbind(funData, Unl2024_raw)

#remove NA values from fund data and select relevant fields
funData <- funData[!is.na(funData$transaction_obligated_amount),]
funData <-select(funData, budget_subfunction, awarding_agency_name, awarding_subagency_name, transaction_obligated_amount, recipient_state, recipient_county, award_type, recipient_name, program_activity_name, cfda_number, cfda_title)
targetE <- c("AL","AR","FL","GA","KY", "LA", "MS", "NC", "SC", "TN", "VA", "GU", "PR", "MP", "AS", "VI")
targetO <- c("GU", "PR", "MP", "AS", "VI")
SETerrData <- dplyr::filter(funData,recipient_state %in% targetE) #filter to SE and territories

# USfundByState <- group_by(funData, recipient_state) %>% dplyr::summarise(
#   StateFunding = sum(transaction_obligated_amount))%>%
#   as.data.frame()
# UStot<- sum(USfundByState$StateFunding)
#group funding by territory/state
fundByState <- group_by(SETerrData, recipient_state) %>% dplyr::summarise(
  StateFunding = sum(transaction_obligated_amount))%>%
  as.data.frame()

colnames(fundByState)[1] <- "STATE"
#join shapefile to data for terr + states
BIL <- left_join(SETerr, fundByState, by = "STATE")

#create targets for each REEO and territories
NEEP <- c("WV","DC","NJ","MD","PA","NY","VT","MA","RI","CT","NH","ME","DE")
SEEA <- c("AR","AL","FL","GA","KY","LA","MS","NC","SC","TN","VA")
MEEA <- c("OH","IN","MI","KS","NE","SD","ND","MN","IA","MO","IL","WI")
SPEER <- c("TX","OK")
SWEEP <- c("NM","AZ","CO","UT","NV","WY")
NEEA <- c("MT","ID","OR","WA")
Territories <- c("PR","AS","GU","MP","VI")
International <- c("FM", "PW","MH")

#summarize by state/territory
funData_national <- funData
funData_national <- funData_national%>% group_by(recipient_state)%>%
  dplyr::summarise(Funding = sum(transaction_obligated_amount)) %>% 
  as.data.frame()

#mark states by their REEO
Region = ifelse(funData_national$recipient_state %in% NEEP,"NEEP","")
funData_national = cbind(Region,funData_national)
funData_national$Region = ifelse(funData_national$recipient_state %in% SEEA,"SEEA",funData_national$Region)
funData_national$Region = ifelse(funData_national$recipient_state %in% MEEA,"MEEA",funData_national$Region)
funData_national$Region = ifelse(funData_national$recipient_state %in% SPEER,"SPEER",funData_national$Region)
funData_national$Region = ifelse(funData_national$recipient_state %in% SWEEP,"SWEEP",funData_national$Region)
funData_national$Region = ifelse(funData_national$recipient_state %in% NEEA,"NEEA",funData_national$Region)
funData_national$Region = ifelse(funData_national$recipient_state == "AK","Alaska",funData_national$Region)
funData_national$Region = ifelse(funData_national$recipient_state == "CA","California",funData_national$Region)
funData_national$Region = ifelse(funData_national$recipient_state == "HI","Hawaii",funData_national$Region)
funData_national$Region = ifelse(funData_national$recipient_state == "","International",funData_national$Region)
funData_national$Region = ifelse(funData_national$recipient_state %in% International,"International",funData_national$Region)
funData_national$Region = ifelse(funData_national$recipient_state %in% Territories,"Territories",funData_national$Region)
perCapita_national <- sum(funData_national$Funding)/333287557
funData_national <- funData_national %>% select(Region, Funding)%>%
  na.omit()%>%
  group_by(Region)%>%
  dplyr::summarise(Funding = sum(Funding)) %>% 
  as.data.frame()
#repeat for grants
funData_nat_grants <- funData
funData_nat_grants <- funData_nat_grants%>% filter(award_type=="COOPERATIVE AGREEMENT (B)"|award_type=="PROJECT GRANT (B)")%>%group_by(recipient_state)%>%
  dplyr::summarise(Funding = sum(transaction_obligated_amount)) %>% 
  as.data.frame()
Region = ifelse(funData_nat_grants$recipient_state %in% NEEP,"NEEP","")
funData_nat_grants = cbind(Region,funData_nat_grants)
funData_nat_grants$Region = ifelse(funData_nat_grants$recipient_state %in% SEEA,"SEEA",funData_nat_grants$Region)
funData_nat_grants$Region = ifelse(funData_nat_grants$recipient_state %in% MEEA,"MEEA",funData_nat_grants$Region)
funData_nat_grants$Region = ifelse(funData_nat_grants$recipient_state %in% SPEER,"SPEER",funData_nat_grants$Region)
funData_nat_grants$Region = ifelse(funData_nat_grants$recipient_state %in% SWEEP,"SWEEP",funData_nat_grants$Region)
funData_nat_grants$Region = ifelse(funData_nat_grants$recipient_state %in% NEEA,"NEEA",funData_nat_grants$Region)
funData_nat_grants$Region = ifelse(funData_nat_grants$recipient_state == "AK","Alaska",funData_nat_grants$Region)
funData_nat_grants$Region = ifelse(funData_nat_grants$recipient_state == "CA","California",funData_nat_grants$Region)
funData_nat_grants$Region = ifelse(funData_nat_grants$recipient_state == "HI","Hawaii",funData_nat_grants$Region)
funData_nat_grants$Region = ifelse(funData_nat_grants$recipient_state == "","International",funData_nat_grants$Region)
funData_nat_grants$Region = ifelse(funData_nat_grants$recipient_state %in% International,"International",funData_nat_grants$Region)
funData_nat_grants$Region = ifelse(funData_nat_grants$recipient_state %in% Territories,"Territories",funData_nat_grants$Region)
#summarize by REEO
funData_nat_grants <- funData_nat_grants %>% select(Region, Funding)%>%
  group_by(Region)%>%
  dplyr::summarise(GrantFunding = sum(Funding)) %>% 
  as.data.frame()

#make pretty for table
# colnames(FunData_national)[2] <- "Funding"
funData_national$Funding <- formattable::currency(funData_national$Funding, digits=0L)

#create REEO targets AGAIN for population data
MEEA1 <- c(".Ohio",".Indiana",".Michigan",".Kansas",".Nebraska",".South Dakota",".North Dakota",".Minnesota",".Iowa",".Missouri",".Illinois",".Wisconsin")
NEEP1 <- c(".West Virginia",".District of Columbia",".New Jersey",".Maryland",".Pennsylvania",".New York",".Vermont",".Massachusetts",".Rhode Island",".Connecticut",".New Hampshire",".Maine",".Delaware")
SEEA1 <- c(".Alabama",".Arkansas",".Florida",".Georgia",".Kentucky",".Louisiana",".Mississippi",".North Carolina",".South Carolina",".Tennessee",".Virginia")
SWEEP1 <- c(".New Mexico",".Arizona",".Colorado",".Utah",".Nevada",".Wyoming")
NEEA1 <- c(".Montana",".Idaho",".Oregon",".Washington")
SPEER1 <- c(".Texas",".Oklahoma")
colnames(pop2022_raw)[1]<- "State"
#mark their REEO
Region = ifelse(pop2022_raw$State %in% NEEP1,"NEEP","")
popRegion = cbind(Region,pop2022_raw)
popRegion$Region = ifelse(popRegion$State %in% SEEA1,"SEEA",popRegion$Region)
popRegion$Region = ifelse(popRegion$State %in% MEEA1,"MEEA",popRegion$Region)
popRegion$Region = ifelse(popRegion$State %in% SPEER1,"SPEER",popRegion$Region)
popRegion$Region = ifelse(popRegion$State %in% SWEEP1,"SWEEP",popRegion$Region)
popRegion$Region = ifelse(popRegion$State %in% NEEA1,"NEEA",popRegion$Region)
popRegion$Region = ifelse(popRegion$State == ".Alaska","Alaska",popRegion$Region)
popRegion$Region = ifelse(popRegion$State == ".California","California",popRegion$Region)
popRegion$Region = ifelse(popRegion$State == ".Hawaii","Hawaii",popRegion$Region)
popRegion$Region = ifelse(popRegion$State == "","International",popRegion$Region)
popRegion$X.3 <- as.numeric(gsub(",","",popRegion$X.3)) #convert to numeric for summing
popRegion <- popRegion %>% select(Region, X.3)%>% #summarize population by region
  group_by(Region)%>%
  dplyr::summarise(Population = sum(X.3)) %>% 
  as.data.frame()

#join shapefile to population data and calculate per capita funding
RegMap <- left_join(funData_national, popRegion, by="Region")
RegMap$perCapita = RegMap$Funding/RegMap$Population
RegMap$perCapita <- formattable::currency(RegMap$perCapita, digits=0L)
#join shapefile to grant data and calculate per capita funding
RegMap <- left_join(RegMap,funData_nat_grants, by="Region")
RegMap$perCapitaGrants = RegMap$GrantFunding/RegMap$Population
RegMap$perCapitaGrants <- formattable::currency(RegMap$perCapitaGrants, digits=0L)
RegMap$GrantFunding <- formattable::currency(RegMap$GrantFunding, digits=0L)

Regiontable<- RegMap%>% select(Region, Funding)
Regiontable%>% kbl(row.names=FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, html_font="Open Sans", font_size = 14)%>%
  add_header_above(c("Funding by Region"=2))%>%
  row_spec(1:11, color  = "black")%>%
  column_spec(1, "12cm")%>%
  column_spec(2, "3cm")
Regiontable
# save_kable(Regiontable,"C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/Regiontable.png")

# ###whitepaper maps
# #experiment with projection
# install.packages("albersusa")
# library(remotes)
# remotes::install_git("https://git.rud.is/hrbrmstr/albersusa.git")
# install.packages("maptools", repos="http://R-Forge.R-project.org")
# library(albersusa)
# alb_usa <- albersusa::usa_sf('laea')%>%
#   select(1:7)
# Region = ifelse(alb_usa$iso_3166_2 %in% NEEP,"NEEP","")
# alb_usa = cbind(Region,alb_usa)
# alb_usa$Region = ifelse(alb_usa$iso_3166_2 %in% SEEA,"SEEA",alb_usa$Region)
# alb_usa$Region = ifelse(alb_usa$iso_3166_2 %in% MEEA,"MEEA",alb_usa$Region)
# alb_usa$Region = ifelse(alb_usa$iso_3166_2 %in% SPEER,"SPEER",alb_usa$Region)
# alb_usa$Region = ifelse(alb_usa$iso_3166_2 %in% SWEEP,"SWEEP",alb_usa$Region)
# alb_usa$Region = ifelse(alb_usa$iso_3166_2 %in% NEEA,"NEEA",alb_usa$Region)
# alb_usa$Region = ifelse(alb_usa$iso_3166_2 == "AK","Alaska",alb_usa$Region)
# alb_usa$Region = ifelse(alb_usa$iso_3166_2 == "CA","California",alb_usa$Region)
# alb_usa$Region = ifelse(alb_usa$iso_3166_2 == "HI","Hawaii",alb_usa$Region)
# alb_usa$Region = ifelse(alb_usa$iso_3166_2 == "","International",alb_usa$Region)
# alb_usa$Region = ifelse(alb_usa$iso_3166_2 %in% International,"International",alb_usa$Region)
# alb_usa$Region = ifelse(alb_usa$iso_3166_2 %in% Territories,"Territories",alb_usa$Region)
# st_write(alb_usa,"C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/albers_us1.shp")
# regions <- st_read("C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/albers_us1_Dissolve.shp")
# #join by FIPS or iso
# Grantsmap_test <- left_join(regions, funData_nat_grants, by="Region")
# Grantsmap_test <- Grantsmap_test[!is.na(Grantsmap_test$Shape_Area),]
# Grantsmap_test2 <- Grantsmap_test
# Grantsmap_test$Region_Name <- c("Alaska","California","Hawaii","Midwest","Northwest","Northeast","Southeast","South Central","Southwest")
# 
# tm_shape(Grantsmap_test) + 
#   tm_polygons("GrantFunding",
#           palette= c("#B8E9F0","#75C7D3", "#00869F", "#00447C"),
#           breaks=c(0, 1000000000,5000000000, 15000000000, Inf),
#           textNA= "$0",
#           labels = c(
#       "$0-1 billion", "$1-5 billion", "$5-15 billion", "$15 billion+"),
#       popup.vars= c("Funding: "="GrantFunding"),
#       popup.format= list(prefix="$", big.num.abbr=NA),
#       id= "Region",
#       alpha=.85,
#       title= "Funding",
#       border.col="white")+
#   tm_borders(col="white", lwd=.25)+
#   tm_text(text="Region_Name",col="#000000", size=1, fontfamily = "Calibri", fontface="bold")+
# tm_shape(Grantsmap_test2)+
#   tm_borders(col="white", lwd=1)+
# tmap_options(check.and.fix = TRUE)+
# tm_layout(main.title = "The Northeast Has Received Far More Grant Funding Than Any \nOther Region",
#       main.title.fontfamily = "Calibri",
#       main.title.fontface = "bold",
#       main.title.size= 1,
#       # asp= 1.5,
#       legend.position= c("right","bottom"),
#       legend.text.fontfamily = "Calibri",
#       legend.title.fontfamily = "Calibri",
#       legend.title.size= 1,
#       legend.text.size=.8,
#       legend.bg.color= "white",
#       legend.bg.alpha=.6)
# tmap_save(filename="C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/Grants_Nat_02_2024v2.png", height=4, width =6, dpi=1200)
# 
# Totalmap <- left_join(regions, funData_national, by="Region")
# Totalmap <- Totalmap[!is.na(Totalmap$Shape_Area),]
# Totalmap2 <- Totalmap
# Totalmap$Region_Name <- c("Alaska","California","Hawaii","Midwest","Northwest","Northeast","Southeast","South Central","Southwest")
# 
# tm_shape(Totalmap) +
#   tm_polygons("Funding",
#           palette= c("#B8E9F0","#75C7D3", "#00869F", "#00447C"),
#           breaks=c(0, 5000000000,20000000000, 40000000000, Inf),
#           textNA= "$0",
#           labels = c(
#       "$0-5 billion", "$5-20 billion", "$20-40 billion", "$40 billion+"),
#       id= "Region",
#       alpha=.85,
#       title= "Funding",
#       border.col="white")+
#   tm_text(text="Region_Name",col="#000000", size=1, fontfamily = "Calibri", fontface="bold")+
#   tm_borders(col="white", lwd=.25)+
# tmap_options(check.and.fix = TRUE)+
# tm_layout(main.title = "The Southeast and Midwest Lag Behind the Northeast in Committed \nFunding Despite Larger Populations",
#       main.title.fontfamily = "Calibri",
#       main.title.fontface = "bold",
#       main.title.size= 1,
#       # asp= 1.5,
#       legend.position= c("right","bottom"),
#       legend.text.fontfamily = "Calibri",
#       legend.title.fontfamily = "Calibri",
#       legend.title.size= 1,
#       legend.text.size=.8,
#       legend.bg.color= "white",
#       legend.bg.alpha=.6)
# 
# tmap_save(filename="C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/Total_Nat_02_2024v2.png", height=4, width =6, dpi=1200)

# totalUS <- sum(Grantsmap$SUM_Fundin)
# SE_perc <- Grantsmap$SUM_Fundin[8]/totalUS*100
# pop2022_raw$X.3 <- gsub(",","",pop2022_raw$X.3)
# USperCap <- totalUS/as.numeric(pop2022_raw$X.3[4])

# DirectSE <- funData%>%filter(award_type=="DIRECT PAYMENT FOR SPECIFIED USE, AS A SUBSIDY OR OTHER NON-REIMBURSABLE DIRECT FINANCIAL AID (C)")%>%
#   filter(recipient_state %in% SEEA)
# DirectSEFCC <- DirectSE%>%filter(awarding_agency_name=="FEDERAL COMMUNICATIONS COMMISSION (FCC)")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}

#select population field
colnames(pop2022_raw)[1] <- "State"
pop2022 <-select(pop2022_raw, State, X.3)

#retrieve total and perCap for US
totalUS <- formattable::currency(sum(funData$transaction_obligated_amount), digits=0L)
pop2022$X.3 <- as.numeric(gsub(",","",pop2022$X.3))
totPopUS <- pop2022$X.3[4]
avgPerCapUS <- formattable::currency(totalUS/totPopUS, digits=0L)

#filter funding and grant data to states and territories
funData <- dplyr::filter(funData, recipient_state %in% targetE)
gTarg <- c("COOPERATIVE AGREEMENT (B)","PROJECT GRANT (B)")
GrantsCA_df <- dplyr::filter(funData, award_type %in% gTarg)%>%
  group_by(recipient_state)%>%
  dplyr::summarise(Funding = sum(transaction_obligated_amount)) %>% 
  as.data.frame()
DataTerr <- dplyr::filter(funData, recipient_state %in% targetO)

#filter pop by state
targetF <- c(".Alabama",".Arkansas",".Florida",".Georgia",".Kentucky", ".Louisiana", ".Mississippi", ".North Carolina", ".South Carolina", ".Tennessee", ".Virginia")
pop2022 <- dplyr::filter(pop2022, State %in% targetF)

#calculate percent and per cap funding
pop2022$State <- c('AL', 'AR', 'FL', 'GA', 'KY', 'LA', 'MS', 'NC', 'SC', 'TN', 'VA')
colnames(pop2022)[1] <- "STATE"
fundByState <- left_join(fundByState, pop2022, by = "STATE") 
fundByState$X.3 <- as.numeric(gsub(",","",fundByState$X.3))
fundByState$perCapita <- fundByState$StateFunding/fundByState$X.3
fundByState$Percent <- fundByState$StateFunding/sum(fundByState$StateFunding)*100
fundByState$Percent <- format(round(fundByState$Percent, 2), nsmall=2)
fundByState$Percent <- as.numeric(fundByState$Percent)
fundByState$StateFunding <- signif(fundByState$StateFunding, 5)
# fundByState$Funding <- formattable::currency(fundByState$Funding, digits = 0L)
fundByState$perCapita <- formattable::currency(fundByState$perCapita, digits = 0L)
pop2022$X.3 <- as.numeric(gsub(",","",pop2022$X.3))
# totPop <- sum(pop2022$X.3)

BIL <- left_join(BIL, pop2022, by = "STATE") 
BIL$perCapita <- BIL$StateFunding/BIL$X.3
BIL$perCapita <- format(round(BIL$perCapita, 2), nsmall=2)
BIL$perCapita <- formattable::currency(BIL$perCapita, digits = 0L)
BIL$StateFunding <- signif(as.numeric(BIL$StateFunding), 5)
```
## Bipartisan Infrastructure Law Funding in the Southeast

```{r, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, results='hide', fig.show='hide'}
BIL$StateFunding <- formattable::currency(BIL$StateFunding)
#tmap
# tmap_mode(mode ="plot")
# bbox_SE <- st_bbox(SEstates)
# 
# # tm_basemap("CartoDB.PositronNoLabels")
# 
# mbtiles <- get_static_tiles(
#   location = c(-100, 23, -67, 40),
#   zoom = 4,
#   style_url= "mapbox://styles/gparker-seea/clkr4hgj800zo01qk7npq3p0x",
#   username="gparker-seea",
#   access_token= "pk.eyJ1IjoiZ3Bhcmtlci1zZWVhIiwiYSI6ImNsa3I0ZHFtajJnc2QzcWtlajlmbWV3d2IifQ.jk6o3SXtTTAneVg11e_pww"
# )
# 
# # tm_shape(territories, is.master=F)+
# #   tm_fill(col="grey70")+
# tm_shape(mbtiles)+
#   tm_rgb() + 
# tm_shape(BIL) +
#   tm_polygons("StateFunding",
#           palette= c("#B8E9F0","#75C7D3", "#00869F", "#00447C"),
#           breaks=c(1000000000, 1500000000, 2000000000, 3000000000, Inf),
#           textNA= "$0",
#           labels = c(
#       "$1-1.5 billion", "$1.5-2 billion", "$2-3 billion", "$3 billion+"),
#       popup.vars= c("Funding: "="StateFunding"),
#       popup.format= list(prefix="$", big.num.abbr=NA),
#       id= "NAME",
#       alpha=.85,
#       title= "BIL State Funding",
#       border.col="white")+
#   tm_borders(col="white", lwd=.25)+
# tm_shape(SEstates)+
#   tm_borders(col="white", lwd=1)+
# tmap_options(check.and.fix = TRUE)+
# tm_layout(main.title = "Bipartisan Infrastructure Law Funding in the Southeast",
#       main.title.fontfamily = "Calibri",
#       main.title.fontface = "bold", 
#       main.title.size= 1,
#       # asp= 1.5,
#       legend.position= c("right","bottom"),
#       legend.text.fontfamily = "Calibri", 
#       legend.title.fontfamily = "Calibri", 
#       legend.title.size= 1)
# 
# tmap_save(filename="C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/funding.png", height=4, width =6, dpi=1200)
```

<div class = "row">
<div class = "col-md-8" style="padding-right:25px;">

```{r,  message=FALSE, warning=FALSE, echo=FALSE, out.width="100%"}
Regional <- RegMap
Regional_Grants <- RegMap
colnames(GrantsCA_df)[1] <-"STATE"
Grantsmap <- left_join(SETerr, GrantsCA_df, by="STATE")
#tmap
tmap_mode(mode ="view")
BILmap <- tm_basemap("CartoDB.PositronNoLabels")+
tm_shape(BIL) +
  tm_polygons("StateFunding",
          palette= c("#75C7D3", "#00869F", "#006A7E", "#00315E"),
          breaks=c(0, 2000000000, 3000000000, 5000000000, Inf),
          textNA= "$0",
          labels = c("$0-2 billion", "$2-3 billion", "$3-5 billion", "$5 billion+"),
      popup.vars= c("Funding: "="StateFunding","Per Capita:"="perCapita"),
      popup.format= list(prefix="$", big.num.abbr=NA),
      id= "NAME",
      title= "Southeast Total",
      border.col="white")+
  tm_shape(Grantsmap) +
  tm_polygons("Funding",
          palette= c("#75C7D3", "#00869F", "#006A7E", "#00315E"),
          breaks=c(0, 200000000, 300000000, 500000000, Inf),
          textNA= "$0",
          labels = c("$0-200 million", "$2-300 million", "$3-500 million", "$500 million+"),
      popup.vars= c("Funding: "="Funding"),
      popup.format= list(prefix="$", big.num.abbr=NA),
      id= "NAME",
      title= "Southeast Grants",
      border.col="white")+
  # tm_shape(Regional) +
  # tm_polygons("Funding",
  #         palette= c("#75C7D3", "#00869F", "#006A7E", "#00315E"),
  #         breaks=c(0, 5000000000,10000000000, 20000000000, Inf),
  #         textNA= "$0",
  #         labels = c("$0-5 billion", "$5-10 billion", "$10-20 billion", "$20 billion+"),
  #     popup.vars= c("Funding: "="Funding"),
  #     popup.format= list(prefix="$", big.num.abbr=NA),
  #     id= "NAME",
  #     title= "Regional Total",
  #     border.col="white")+
  # tm_shape(Regional_Grants) +
  # tm_polygons("Funding",
  #         palette= c("#75C7D3", "#00869F", "#006A7E", "#00315E"),
  #         breaks=c(0, 500000000,1000000000, 5000000000, Inf),
  #         textNA= "$0",
  #         labels = c("$0-500 million", "$.5-1 billion", "$1-5 billion", "$5 billion+"),
  #     popup.vars= c("Funding: "="Funding"),
  #     popup.format= list(prefix="$", big.num.abbr=NA),
  #     id= "NAME",
  #     title= "Regional Grants",
  #     border.col="white")+
  # tm_borders(col="white", lwd=.25)+
tmap_options(check.and.fix = TRUE, output.size=50)+
tm_layout(main.title = "Bipartisan Infrastructure Law Funding in the Southeast",
      main.title.fontfamily = "Open Sans",
      main.title.fontface = "bold", 
      main.title.size= 1,
      asp= 1.5,
      legend.text.fontfamily = "Open Sans", 
      legend.title.fontfamily = "Open Sans", 
      legend.title.size= 1)+
  tm_view(set.view=c(-85.2,35,5))
BILmap
# BILmap %>% 
#   tmap_leaflet() %>%
#   leaflet::hideGroup("Grants")

#tmap COOP AGREEMENTS AND GRANTS
# colnames(Grants)[1] <- "STATE"
# Grants <- left_join(SETerr, Grants, by="STATE")
# Grants$Funding <- formattable::currency(Grants$Funding)
# # Grants <- left_join(SETerr, Grants, by = "FIPS")
# tmap_mode(mode ="view")
# tm_basemap("CartoDB.PositronNoLabels")+
# tm_shape(Grants) +
#   tm_polygons("Funding",
#           palette= c("#75C7D3", "#00869F", "#006A7E", "#00315E"),
#           breaks=c(0, 100000000, 150000000, 200000000, Inf),
#           textNA= "$0",
#           labels = c("$0-50 million", "$50-100 million", "$100-200 million", "$200 million+"),
#       popup.vars= c("Funding: "="Funding"),
#       popup.format= list(prefix="$", big.num.abbr=NA),
#       id= "NAME",
#       title= "BIL Cooperative Agreement and Grant Funding",
#       border.col="white")+
#   tm_borders(col="white", lwd=.25)+
# tmap_options(check.and.fix = TRUE, output.size=50)+
# tm_layout(main.title = "BIL Cooperative Agreement and Grant Funding",
#       main.title.fontfamily = "Open Sans",
#       main.title.fontface = "bold", 
#       main.title.size= 1,
#       asp= 1.5,
#       legend.text.fontfamily = "Open Sans", 
#       legend.title.fontfamily = "Open Sans", 
#       legend.title.size= 1)+
#   tm_view(set.view=c(-85.2,35,5))
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, results='hide', fig.show='hide'}

# tmap_mode(mode ="plot")
# bbox_SE <- st_bbox(SEstates)
# 
# # tm_basemap("CartoDB.PositronNoLabels")
# 
# mbtiles <- get_static_tiles(
#   location = c(-100, 23, -67, 40),
#   zoom = 4,
#   style_url= "mapbox://styles/gparker-seea/clkr4hgj800zo01qk7npq3p0x",
#   username="gparker-seea",
#   access_token= "pk.eyJ1IjoiZ3Bhcmtlci1zZWVhIiwiYSI6ImNsa3I0ZHFtajJnc2QzcWtlajlmbWV3d2IifQ.jk6o3SXtTTAneVg11e_pww"
# )
# 
# # tm_shape(territories, is.master=F)+
# #   tm_fill(col="grey70")+
# tm_shape(mbtiles)+
#   tm_rgb() +
# tm_shape(BIL) +
#   tm_polygons("StateFunding",
#           palette= c("#B8E9F0","#75C7D3", "#00869F", "#00447C"),
#           breaks=c(0, 2000000000, 3000000000, 5000000000, Inf),
#           textNA= "$0",
#           labels = c(
#       "$1.5-2 billion", "$2-3 billion", "$3-5 billion", "$5 billion+"),
#       popup.vars= c("Funding: "="StateFunding"),
#       popup.format= list(prefix="$", big.num.abbr=NA),
#       id= "NAME",
#       alpha=.85,
#       title= "BIL State Funding",
#       border.col="white")+
#   tm_borders(col="white", lwd=.25)+
# tm_shape(SEstates)+
#   tm_borders(col="white", lwd=1)+
# tmap_options(check.and.fix = TRUE)+
# tm_layout(main.title = "Bipartisan Infrastructure Law Funding in the Southeast",
#       main.title.fontfamily = "Calibri",
#       main.title.fontface = "bold",
#       main.title.size= 1,
#       # asp= 1.5,
#       legend.position= c("right","bottom"),
#       legend.text.fontfamily = "Calibri",
#       legend.title.fontfamily = "Calibri",
#       legend.title.size= 1)
# 
# tmap_save(filename="C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/SE_total_02_2024.png", height=4, width =6, dpi=1200)

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, results='hide', fig.show='hide'}

#tmap
# tmap_mode(mode ="plot")
# bbox_SE <- st_bbox(SEstates)
# 
# # tm_basemap("CartoDB.PositronNoLabels")
# 
# mbtiles <- get_static_tiles(
#   location = c(-100, 23, -67, 40),
#   zoom = 4,
#   style_url= "mapbox://styles/gparker-seea/clkr4hgj800zo01qk7npq3p0x",
#   username="gparker-seea",
#   access_token= "pk.eyJ1IjoiZ3Bhcmtlci1zZWVhIiwiYSI6ImNsa3I0ZHFtajJnc2QzcWtlajlmbWV3d2IifQ.jk6o3SXtTTAneVg11e_pww"
# )

# tm_shape(territories, is.master=F)+
#   tm_fill(col="grey70")+
# tm_shape(mbtiles)+
#   tm_rgb() +
# tm_shape(Grantsmap) +
#   tm_polygons("Funding",
#           palette= c("#B8E9F0","#75C7D3", "#00869F", "#00447C"),
#           breaks=c(0, 200000000, 300000000, 500000000, Inf),
#           textNA= "$0",
#           labels = c(
#       "$0-200 million", "$200-300 million", "$300-500 million", "$500 million+"),
#       popup.vars= c("Funding: "="Funding"),
#       popup.format= list(prefix="$", big.num.abbr=NA),
#       id= "STATE",
#       alpha=.85,
#       title= "Funding",
#       border.col="white")+
#   tm_borders(col="white", lwd=.25)+
# tm_shape(SEstates)+
#   tm_borders(col="white", lwd=1)+
# tmap_options(check.and.fix = TRUE)+
# tm_layout(main.title = "Grants and Cooperative Agreements",
#       main.title.fontfamily = "Calibri",
#       main.title.fontface = "bold",
#       main.title.size= 1,
#       # asp= 1.5,
#       legend.position= c("right","bottom"),
#       legend.text.fontfamily = "Calibri",
#       legend.title.fontfamily = "Calibri",
#       legend.title.size= 1)
# # 
# tmap_save(filename="C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/Grants_SE_02_2024.png", height=4, width =6, dpi=1200)

# RegMap$Region[5] <- "Midwest"
# RegMap$Region[6] <- "Northwest"
# RegMap$Region[7] <- "Northeast"
# RegMap$Region[8] <- "Southeast"
# RegMap$Region[9] <- "South Central"
# RegMap$Region[10] <- "Southwest"
# RegMap <- RegMap[!is.na(RegMap$Population),]
# RegMap <- RegMap[order(RegMap$Funding,decreasing=TRUE),]%>%as.data.frame()%>%
#   select(Region, Funding, perCapita, GrantFunding, perCapitaGrants)
# colnames(RegMap)[3] <-"Total Per Capita"
# colnames(RegMap)[4] <- "Grant Funding"
# colnames(RegMap)[5] <- "Grants Per Capita"
# RegionTable<- RegMap%>% kbl(row.names=FALSE) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, html_font="Calibri", font_size = 14, position="center", row_label_position = r)%>%
#   add_header_above(c("Funding by Region"=5))%>%
#   row_spec(1:9, color  = "#444444")%>%
#   column_spec(1:5, "3cm")
# RegionTable
# 
# save_kable(RegionTable,"C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/Regiontable_02_2024.png")
```
</div>

<div class = "col-md-4">
<br>
The [Infrastructure Investment and Jobs Act](https://www.congress.gov/bill/117th-congress/house-bill/3684), also known as the Bipartisan Infrastructure Law (BIL), was passed in November 2021 and allocates $1.2 trillion over ten years in funding for infrastructure projects including roads, public transit, broadband, and electric grid upgrades. As federal agencies continue to allocate BIL funding, this map shows how much funding recipients in the Southeast have received as of January 22, 2024. This dashboard focuses on funding available through the BIL, and we plan to address additional sources of funding, including the Inflation Reduction Act (IRA) in future versions of this whitepaper as more funding is allocated.
<br>
</div>

## {.tabset .tabset-row2}
### Funding By State
```{css, echo=FALSE}
.nav-row2>li>a {
  background-color: #fff; /* Change "yourcolor" to the desired color value */
  color: #444444; /* Change the tab text color if needed */
}

.nav-row2>li.active>a,
.nav-row2>li.active>a:hover,
.nav-row2>li.active>a:focus {
  background-color: #75c7d3; /* Change "youractivecolor" to the desired active color value */
  color: #444444; /* Change the active tab text color if needed */
}
```

#### {.tabset .tabset-row2}
##### Overview
<div class = "row">
<div class = "col-md-7" style="padding-right:25px;">
```{r echo=FALSE}
targetM <- c("AL","AR","FL","GA","KY", "LA", "MS", "NC", "SC", "TN", "VA")
SEdata<- filter(fundByState, STATE %in% targetM)
SEdata$State <- c("Alabama","Arkansas","Florida","Georgia","Kentucky", "Louisiana", "Mississippi", "North Carolina", "South Carolina", "Tennessee", "Virginia")
colnames(SEdata)[2] <- "Funding"
SEdata <- SEdata[order(SEdata$Funding,decreasing=TRUE),]
SEdata$zone.start <- with(SEdata, c(0, cumsum(Percent)[-length(Percent)]))
SEdata$zone.end <- with(SEdata, cumsum(Percent))
SEdata$label.point <- with(SEdata, ((zone.start + zone.end) / 2))
# 
pie <- ggplot(SEdata, aes(x="", y=Percent, fill=reorder(State, Percent, decreasing=F)))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start=0)+
  scale_fill_manual(values=c("#BFBFBF", "#6171AF", "#00869F", "#75C7D3", "#AAC5E2", "#8FED94", "#FFF7B3","#FCB616", "#D4442D", "#C70039", "#900C3F"), name= "States")+
  geom_text_repel(data = SEdata,
                   aes(y = label.point, label = ifelse(Percent>10,paste0(Percent, "%"),""), family="Open Sans"),
  size = 4.5, color="#444444", nudge_x = 1, show.legend = FALSE) +
  ggtitle("Southeast BIL Funding by State")+
  theme_void(base_family="Open Sans")+
  guides(fill=guide_legend(reverse=T))+ 
  theme(legend.text=element_text(size=12, color="#444444"), 
       plot.title = element_text(color = "#444444"), 
       legend.title = element_text(color = "#444444"))
pie


SEdata <- SEdata[order(SEdata$Funding,decreasing=TRUE),]
# SEdata$zone.start <- with(SEdata, c(0, cumsum(Percent)[-length(Percent)]))
# SEdata$zone.end <- with(SEdata, cumsum(Percent))
# SEdata$label.point <- with(SEdata, ((zone.start + zone.end) / 2))
SEdata$color <- c("#BFBFBF", "#6171AF", "#00869F", "#75C7D3", "#AAC5E2", "#8FED94", "#FFF7B3","#FCB616", "#D4442D", "#C70039", "#900C3F")
SEdata$label <- paste(SEdata$State, SEdata$Percent, "%", sep=" ")
# library(treemap)
# tm <- treemap(
#   dtf = SEdata,
#   index = "label",
#   vSize = "Funding",
#   vColor = "color",
#   type = 'color', # {treemap}'s equivalent of scale_fill_identity() 
#   title="Funding Varies Drastically Among States in the Southeast",
#   fontfamily.title= "Calibri",
#   fontfamily.labels= "Calibri",
#   border.col="white",
#   border.lwds=3
# )
# tm
# total <- formattable::currency(sum(fundByState$Funding), digits=0L)
# SEpercent <- as.numeric(total)/as.numeric(totalUS)*100
# SEpercent <- format(round(SEpercent, 2), nsmall=2)
# avgPerCap <- formattable::currency(total/totPop, digits=0L)
# SEpercPop <- as.numeric(totPop)/as.numeric(totPopUS)*100
# SEpercPop <- format(round(SEpercPop, 2), nsmall=2)
# 
# 

#EXPERIMENT
# library(highcharter)
# library(magrittr)
# 
# # set options
# hcoptslang <- getOption("highcharter.lang")
# hcoptslang$thousandsSep <- ","
# options(highcharter.lang = hcoptslang)
# 
# colors <- c("#BFBFBF", "#6171AF", "#00869F", "#75C7D3", "#AAC5E2", "#8FED94", "#FFF745","#FCB616", "#D4442D", "#C70039", "#900C3F")
# mytheme <- hc_theme(style = list(fontFamily = "Opens Sans"))
# 
# hc1 <- USmap %>%
#   hchart(
#     "pie", hcaes(x = State, y = Funding),
#     name = "Funding ($)",
#     tooltip= list(formattable::currency(SEdata$Funding,digits=0L)))%>%
#     hc_colors(colors)%>%
#     hc_plotOptions(pie=list(
#       dataLabels = list(enabled = FALSE)
#       ))%>%
#     hc_title(
#     text = "Southeast Funding by State",
#     margin = 20,
#     align = "left",
#     style=list(fontFamily="Opens Sans"))
#     # hc_size(height=400,width=400)
# hc1
```


``` {r echo=FALSE, fig.align='center'}


# colors <- c("#FFA07A","#F08080", "#900C3F", "#C70039", "#D4442D", "#FCB616","#FFF7B3","#8FED94", "#52BE80", "#AAC5E2", "#75C7D3", "#00869F", "#6171AF","#DCB6D0","#C799C8", "#D2D2D2", "#7B7B7B","#585757")
# funcSE$Funding <- signif(as.numeric(funcSE$Funding), 5)
# hc2 <- funcSE %>%
#   hchart(
#     "pie", hcaes(x = budget_subfunction, y = Funding),
#     name = "Funding ($)",
#     tooltip= list(formattable::currency(funcSE$Funding,digits=0L)))%>%
#     hc_colors(colors)%>%
#     hc_plotOptions(pie=list(
#       dataLabels = list(enabled = FALSE)
#       ))%>%
#     hc_title(
#     text = "Southeast Funding by Category",
#     margin = 20,
#     align = "left"
#   )
#     # hc_size(height=400,width=400)



# colors <- c("#900C3F", "#C70039", "#D4442D", "#FCB616", "#52BE80", "#AAC5E2", "#75C7D3", "#00869F", "#6171AF","#DCB6D0","#C799C8", "#D2D2D2", "#7B7B7B","#585757")
# fundByType$Funding <- signif(as.numeric(fundByType$Funding), 5)
# hc3 <- fundByType %>%
#   hchart(
#     "pie", hcaes(x = Type, y = Funding),
#     name = "Funding ($)",
#     tooltip= list(formattable::currency(fundByType$Funding,digits=0L)))%>%
#     hc_colors(colors)%>%
#     hc_plotOptions(pie=list(
#       dataLabels = list(enabled = FALSE)
#       ))%>%
#     hc_title(
#     text = "Southeast Funding by Type",
#     margin = 20,
#     align = "left"
#   )
#     # hc_size(height=400,width=400)

# hw_grid(hc1,hc2,hc3)
# dirSpecUse <- dplyr::filter(funData, grepl("DIRECT PAYMENT FOR SPECIFIED USE", award_type))
# FCC <- dplyr::filter(dirSpecUse, awarding_agency_name == "FEDERAL COMMUNICATIONS COMMISSION (FCC)")
# totaldirSpec <- sum(dirSpecUse$transaction_obligated_amount)
# totalFCC <-  sum(FCC$transaction_obligated_amount)
# percentFCC <- totalFCC/totaldirSpec *100
```
</div>

<div class = "col-md-5">
``` {r echo=FALSE}
# SEdata <- SEdata[order(SEdata$Funding,decreasing=TRUE),]
# SEdata$Funding<- formattable::currency(SEdata$Funding, digits=0L)
# 
# funData_SE_grants <- funData
# funData_SE_grants <- funData_SE_grants%>% filter(award_type=="COOPERATIVE AGREEMENT (B)"|award_type=="PROJECT GRANT (B)")%>%group_by(recipient_state)%>%
#   dplyr::summarise(Funding = sum(transaction_obligated_amount)) %>%
#   as.data.frame()
# funData_SE_grants$Funding <- signif(funData_SE_grants$Funding,5)
# funData_SE_grants$Funding<- formattable::currency(funData_SE_grants$Funding, digits=0L)
# funData_SE_grants <- funData_SE_grants %>% filter(recipient_state %in% targetM)
# 
# funData_SE_grants$State <- c("Alabama","Arkansas","Florida","Georgia","Kentucky", "Louisiana", "Mississippi", "North Carolina", "South Carolina", "Tennessee", "Virginia")
# SEdata <- left_join(SEdata,funData_SE_grants, by="State")
# SEdata$GrantsPerCap = SEdata$Funding.y/SEdata$X.3
# SEdata$GrantsPerCap<- formattable::currency(SEdata$GrantsPerCap, digits=0L)
# 
# SEdata <- SEdata%>% select(State, Funding.x, perCapita, Funding.y, GrantsPerCap)
# colnames(SEdata)[2] <- "Funding"
# colnames(SEdata)[3] <- "Total Per Capita"
# colnames(SEdata)[4] <- "Grant Funding"
# colnames(SEdata)[5] <- "Grants Per Capita"
# statesTable <- SEdata %>% kbl(row.names=FALSE) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, html_font="Open Sans", font_size = 14, position="center", row_label_position = r)%>%
#   add_header_above(c("Southeast Funding by State"=5))%>%
#   row_spec(1:11, color  = "#444444")%>%
#   column_spec(1:5, "3cm")
# statesTable
# # #
# save_kable(statesTable,"C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/Statetable_02_2024.png")

# deoblig <- filter(funData, transaction_obligated_amount < 0)%>%
#   filter(recipient_state %in% targetM)
# 
# deoblig1 <- deoblig %>%
#   group_by(recipient_state) %>% dplyr::summarise(
#   Funding = sum(transaction_obligated_amount)
#   )%>% as.data.frame()
# 
# deTot <- sum(deoblig1$Funding)
# 
# deoblig1$Percent <- 100*(deoblig1$Funding/sum(deoblig1$Funding))
# deoblig1$Percent <- format(round(deoblig1$Percent, 2), nsmall=2)
# deoblig1$Percent <- as.numeric(deoblig1$Percent)
# 
# deoblig1$zone.start <- with(deoblig1, c(0, cumsum(Percent)[-length(Percent)]))
# deoblig1$zone.end <- with(deoblig1, cumsum(Percent))
# deoblig1$label.point <- with(deoblig1, (100-(zone.start + zone.end) / 2))
# 
# colnames(deoblig1)[1] <- "State"
# 
# pie <- ggplot(deoblig1, aes(x="", y=Percent, fill=State))+
#   geom_bar(width = 1, stat = "identity")+
#   coord_polar("y", start=0)+
#   scale_fill_manual(values=c("#FFA07A","#900C3F", "#C70039", "#D4442D", "#00869F", "#6171AF","#DCB6D0","#C799C8", "#D2D2D2", "#7B7B7B","#585757","#17202A")) +
#   geom_text_repel(data = deoblig1,
#                    aes(y = label.point, label = ifelse(Percent>10,paste0(Percent, "%"),""), family="Open Sans"),
#                    size = 4.5, nudge_x = 1, show.legend = FALSE) +
#   ggtitle("Southeast Deobligated Funding by State")+
#   theme_void(base_family= "Open Sans")+
#   theme(legend.key.height = unit(.5,'cm'),
#         legend.key.width = unit(.5, 'cm'))
# pie
# deoblig1$Funding <- formattable::currency(deoblig1$Funding, digits = 0L)
# deoblig1$State[1] <- "Alabama"
# deoblig1$State[2] <- "Arkansas"
# deoblig1$State[3] <- "Florida"
# deoblig1$State[4] <- "Georgia"
# deoblig1$State[5] <- "Kentucky"
# deoblig1$State[6] <- "Louisiana"
# deoblig1$State[7] <- "Mississippi"
# deoblig1$State[8] <- "North Carolina"
# deoblig1$State[9] <- "South Carolina"
# deoblig1$State[10] <- "Tennessee"
# deoblig1$State[11] <- "Virginia"
# deoblig1$Funding <- abs(deoblig1$Funding)
# deoblig1 <- deoblig1[order(deoblig1$Funding,decreasing=TRUE),]
# deoblig1$Funding <- signif(deoblig1$Funding,3)
# DeobTable<- deoblig1%>%select(State, Funding)%>% kbl(row.names=FALSE) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, html_font="Calibri", font_size = 14, position="center", row_label_position = r)%>%
#   add_header_above(c("Deobligated Funding by State"=2))%>%
#   row_spec(1:11, color  = "#444444")%>%
#   column_spec(1:2, "3cm")
# DeobTable
# total_deob <- sum(deoblig1$Funding)
# save_kable(DeobTable,"C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/Deobtable_02_2024.png")
# 
# #By Category
# deoblig2 <- deoblig %>%
#   group_by(budget_subfunction) %>% dplyr::summarise(
#   Funding = sum(transaction_obligated_amount)
#   )%>% as.data.frame()
# 
# deoblig2$Percent <- 100*(deoblig2$Funding/sum(deoblig2$Funding))
# deoblig2$Percent <- format(round(deoblig2$Percent, 2), nsmall=2)
# deoblig2$Percent <- as.numeric(deoblig2$Percent)
# 
# #by Type
# deoblig3 <- deoblig %>%
#   group_by(award_type) %>%
#   dplyr::summarise(
#   Funding = sum(transaction_obligated_amount)
#   )%>% as.data.frame()
# 
# deoblig3$Percent <- 100*(deoblig3$Funding/sum(deoblig3$Funding))
# deoblig3$Percent <- format(round(deoblig3$Percent, 2), nsmall=2)
# deoblig3$Percent <- as.numeric(deoblig3$Percent)
```
</div>

##### Alabama

<div class = "row">
<div class = "col-md-7" style="padding-right:25px;">
```{r, echo=FALSE, fig.align='center'}
#function and award type data, filter to Alabama
funcAL <-dplyr::filter(funData, recipient_state=="AL")%>%
  group_by(budget_subfunction) %>% dplyr::summarise(
  Funding = sum(transaction_obligated_amount)
  )%>% as.data.frame()

funcAL$Percent <- 100*(funcAL$Funding/sum(funcAL$Funding))
funcAL$Percent <- format(round(funcAL$Percent, 2), nsmall=2)
funcAL$Percent <- as.numeric(funcAL$Percent)

funcAL$zone.start <- with(funcAL, c(0, cumsum(Percent)[-length(Percent)]))
funcAL$zone.end <- with(funcAL, cumsum(Percent))
funcAL$label.point <- with(funcAL, (100-(zone.start + zone.end) / 2))

colnames(funcAL)[1] <- "Category"

pie <- ggplot(funcAL, aes(x="", y=Percent, fill=Category))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start=0)+
  scale_fill_manual(values=c("#FFA07A","#F08080","#900C3F","#C70039", "#D4442D", "#8FED94", "#00869F", "#6171AF","#DCB6D0","#C799C8","#D2D2D2","#7B7B7B","#585757")) +
  geom_text_repel(data = funcAL,
                   aes(y = label.point, label = ifelse(Percent>10,paste0(Percent, "%"),""), family="Open Sans"),
                   size = 4.5, color="#444444", nudge_x = 1, show.legend = FALSE)+
  ggtitle("Alabama Funding by Category")+
  theme_void(base_family = "Open Sans")+
  theme(legend.text=element_text(size=12, color="#444444"), 
       plot.title = element_text(color = "#444444"), 
       legend.title = element_text(color = "#444444"))
pie

# colors <- c("#FFA07A","#900C3F","#C70039", "#D4442D", "#8FED94", "#00869F", "#6171AF","#DCB6D0","#C799C8","#7B7B7B","#585757")
funcAL$Funding <- signif(funcAL$Funding, 5)
# hc <- funcAL %>%
#   hchart(
#     "pie", hcaes(x = Category, y = Funding),
#     name = "Funding ($)",
#     tooltip= list(formattable::currency(funcAL$Funding,digits=0L)))%>%
#     hc_colors(colors)%>%
#     hc_plotOptions(pie=list(
#       dataLabels = list(enabled = FALSE)
#       ))%>%
#     hc_size(height=400,width=400)%>%
#     hc_title(
#     text = "Alabama Funding by Category",
#     margin = 20,
#     align = "left"
#   )
# hc


```
</div>

<div class = "col-md-5">
```{r, echo=FALSE, fig.align='center'}
funcAL <- funcAL %>% add_row(Category = "Total", Funding=sum(funcAL$Funding))
funcAL$Funding <- signif(funcAL$Funding, 5)
funcAL$Funding <- currency(funcAL$Funding, digits = 0L)
funcAL%>% select(Category, Funding)%>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, html_font="Open Sans", font_size = 14)%>%
  add_header_above(c("Alabama Funding by Category"=2))%>%
  row_spec(1:13, color  = "#444444")%>%
  column_spec(1, "10cm")%>%
  column_spec(2, "3cm")
```
</div>

<h4>Spotlight on Projects</h4>
Anovion: The Department of Energy committed $117 million to Anovion to build a facility in Colbert County, Alabama, that can produce 35,000 tons annually of synthetic graphite anode material, which is used for EV and critical energy storage lithium-ion batteries. This grant will also be used in part to expand capacity at Anovion’s plant in New York.

City of Birmingham: The Department of Transportation committed $800,000 to the City of Birmingham, Alabama, to study and produce recommendations about how to reduce the negative impacts of rail and highway infrastructure on historically Black communities and historic neighborhoods in general.

##### Arkansas 
<div class = "row">
<div class = "col-md-7" style="padding-right:25px;">
```{r, echo=FALSE, fig.align='center'}
funcAR <-dplyr::filter(funData, recipient_state=="AR")%>%
  group_by(budget_subfunction) %>% dplyr::summarise(
  Funding = sum(transaction_obligated_amount)
  )%>% as.data.frame()

funcAR$Percent <- 100*(funcAR$Funding/sum(funcAR$Funding))
funcAR$Percent <- format(round(funcAR$Percent, 2), nsmall=2)
funcAR$Percent <- as.numeric(funcAR$Percent)

funcAR$zone.start <- with(funcAR, c(0, cumsum(Percent)[-length(Percent)]))
funcAR$zone.end <- with(funcAR, cumsum(Percent))
funcAR$label.point <- with(funcAR, (100-(zone.start + zone.end) / 2))

colnames(funcAR)[1] <- "Category"

pie <- ggplot(funcAR, aes(x="", y=Percent, fill=Category))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start=0)+
  scale_fill_manual(values=c("#FFA07A", "#900C3F", "#C70039", "#D4442D","#FFF7B3","#75C7D3", "#00869F","#6171AF","#DCB6D0","#D2D2D2","#7B7B7B","#585757")) +
  geom_text_repel(data = funcAR,
                   aes(y = label.point, label = ifelse(Percent>10,paste0(Percent, "%"),""),family="Open Sans"),
size = 4.5, color="#444444", nudge_x = 1, show.legend = FALSE) +
  ggtitle("Arkansas Funding by Category")+
  theme_void(base_family="Open Sans")+
    theme(legend.text=element_text(size=12, color="#444444"), 
       plot.title = element_text(color = "#444444"), 
       legend.title = element_text(color = "#444444"))
pie

# colors <- c("#FFA07A", "#900C3F", "#C70039", "#D4442D","#75C7D3", "#00869F","#6171AF","#DCB6D0", "#7B7B7B","#585757")
funcAR$Funding <- signif(funcAR$Funding, 5)
# hc <- funcAR %>%
#   hchart(
#     "pie", hcaes(x = Category, y = Funding),
#     name = "Funding ($)",
#     tooltip= list(formattable::currency(funcAR$Funding,digits=0L)))%>%
#     hc_colors(colors)%>%
#     hc_plotOptions(pie=list(
#       dataLabels = list(enabled = FALSE)
#       ))%>%
#     hc_size(height=400,width=400)%>%
#     hc_title(
#     text = "Arkansas Funding by Category",
#     margin = 20,
#     align = "left"
#   )
# hc
```
</div>
<div class = "col-md-5">
```{r, echo=FALSE, fig.align='center'}
funcAR <- funcAR %>% add_row(Category = "Total", Funding=sum(funcAR$Funding))
funcAR$Funding <- signif(funcAR$Funding, 5)
funcAR$Funding <- currency(funcAR$Funding, digits = 0L)
funcAR%>% select(Category, Funding)%>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, html_font="Open Sans", font_size = 14)%>%
  add_header_above(c("Arkansas Funding by Category"=2))%>%
  row_spec(1:12, color  = "#444444")%>%
  column_spec(1, "10cm")%>%
  column_spec(2, "3cm")
```
</div>
<h4>Spotlight on Projects</h4>
Arkansas Black Mayor’s Association (ABMA): The Natural Resources Conservation Service committed $62.1 million to the ABMA for watershed protection and flood prevention in several cities across the state. 

Westminster Village of the Mid-South: The Environmental Protection Agency committed $1 million to a retirement community in Blytheville, Arkansas, that provides affordable housing on a former air force base, a site contaminated with inorganic substances. The grant will help the nonprofit clean up the site to enhance the safety of its residents.


##### Florida
<div class = "row">
<div class = "col-md-7" style="padding-right:25px;">
```{r, echo=FALSE, fig.align='center'}

#function and award type data, filter to Florida
funcFL <-dplyr::filter(funData, recipient_state=="FL")%>%
  group_by(budget_subfunction) %>% dplyr::summarise(
  Funding = sum(transaction_obligated_amount)
  )%>% as.data.frame()

funcFL$Percent <- 100*(funcFL$Funding/sum(funcFL$Funding))
funcFL$Percent <- format(round(funcFL$Percent, 2), nsmall=2)
funcFL$Percent <- as.numeric(funcFL$Percent)

funcFL$zone.start <- with(funcFL, c(0, cumsum(Percent)[-length(Percent)]))
funcFL$zone.end <- with(funcFL, cumsum(Percent))
funcFL$label.point <- with(funcFL, (100-(zone.start + zone.end) / 2))

colnames(funcFL)[1] <- "Category"

pie <- ggplot(funcFL, aes(x="", y=Percent, fill=Category))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start=0)+
  scale_fill_manual(values=c("#FFA07A", "#900C3F","#C70039", "#D4442D","#FFF7B3","#52BE80", "#75C7D3","#154360","#00869F", "#6171AF","#DCB6D0","#C799C8", "#D2D2D2", "#7B7B7B","#585757", "#000000" )) +
  geom_text_repel(data = funcFL,
                   aes(y = label.point, label = ifelse(Percent>10,paste0(Percent, "%"),""), family="Open Sans"),
size = 4.5, color="#444444", nudge_x = 1, show.legend = FALSE) +
  ggtitle("Florida Funding by Category")+
  theme_void(base_family="Open Sans")+
  theme(legend.text=element_text(size=12, color="#444444"), 
       plot.title = element_text(color = "#444444"), 
       legend.title = element_text(color = "#444444"))
pie

# colors <- c("#FFA07A", "#900C3F","#C70039", "#D4442D","#52BE80", "#75C7D3","#00869F", "#6171AF","#DCB6D0","#C799C8", "#D2D2D2", "#7B7B7B","#585757")
funcFL$Funding <- signif(funcFL$Funding, 5)
# hc <- funcFL %>%
#   hchart(
#     "pie", hcaes(x = Category, y = Funding),
#     name = "Funding ($)",
#     tooltip= list(formattable::currency(funcFL$Funding,digits=0L)))%>%
#     hc_colors(colors)%>%
#     hc_plotOptions(pie=list(
#       dataLabels = list(enabled = FALSE)
#       ))%>%
#     hc_size(height=400,width=400)%>%
#     hc_title(
#     text = "Florida Funding by Category",
#     margin = 20,
#     align = "left"
#   )
# hc
```
</div>
<div class = "col-md-5">
```{r, echo=FALSE, fig.align='center'}
funcFL <- funcFL %>% add_row(Category = "Total", Funding=sum(funcFL$Funding))
funcFL$Funding <- signif(funcFL$Funding, 5)
funcFL$Funding <- currency(funcFL$Funding, digits = 0L)
funcFL%>% select(Category, Funding)%>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, html_font="Open Sans", font_size = 14)%>%
  add_header_above(c("Florida Funding by Category"=2))%>%
  row_spec(1:16, color  = "#444444")%>%
  column_spec(1, "10cm")%>%
  column_spec(2, "3cm")
```
</div>
<h4>Spotlight on Projects</h4>
Central Florida Regional Transportation Authority (CFRTA): The Federal Transit Authority committed $16.1 million to CFRTA in Orlando, Florida to buy battery electric buses and charging infrastructure.

Army Corps of Engineers (ACE) South Florida Ecosystem Restoration Program: The ACE committed $1.1 billion to reconnect habitats in the Everglades, which have been isolated by the impacts of human development. According to the Biden Administration, this is the single largest investment in Everglade’s’ history.

Seminole Tribe of Florida: The Department of Commerce committed about $500,000 to the Seminole Tribe of Florida to establish a digital training program and provide broadband equipment to support schools, libraries, and workforce development.
</div>

##### Georgia
<div class = "row">
<div class = "col-md-7" style="padding-right:25px;">
```{r, echo=FALSE, fig.align='center'}
#function and award type data, filter to Georgia
funcGA <-dplyr::filter(funData, recipient_state=="GA")%>%
  group_by(budget_subfunction) %>% dplyr::summarise(
  Funding = sum(transaction_obligated_amount)
  )%>% as.data.frame()

funcGA$Percent <- 100*(funcGA$Funding/sum(funcGA$Funding))
funcGA$Percent <- format(round(funcGA$Percent, 2), nsmall=2)
funcGA$Percent <- as.numeric(funcGA$Percent)

funcGA$zone.start <- with(funcGA, c(0, cumsum(Percent)[-length(Percent)]))
funcGA$zone.end <- with(funcGA, cumsum(Percent))
funcGA$label.point <- with(funcGA, (100-(zone.start + zone.end) / 2))

colnames(funcGA)[1] <- "Category"

pie <- ggplot(funcGA, aes(x="", y=Percent, fill=Category))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start=0)+
  scale_fill_manual(values=c("#FFA07A","#F08080", "#900C3F", "#C70039", "#D4442D","#FFF7B3","#52BE80","#AAC5E2","#75C7D3", "#00869F", "#6171AF","#DCB6D0","#C799C8", "#D2D2D2", "#7B7B7B","#585757")) +
  geom_text_repel(data = funcGA,
                   aes(y = label.point, label = ifelse(Percent>10,paste0(Percent, "%"),""),family="Open Sans"),
size = 4.5, color="#444444", nudge_x = 1, show.legend = FALSE) +
  ggtitle("Georgia Funding by Category")+
  theme_void(base_family="Open Sans")+
  theme(legend.text=element_text(size=12, color="#444444"), 
       plot.title = element_text(color = "#444444"), 
       legend.title = element_text(color = "#444444"))
pie

# colors <- c("#FFA07A","#F08080", "#900C3F", "#C70039", "#D4442D","#FFF7B3","#52BE80","#75C7D3", "#00869F", "#6171AF","#DCB6D0","#C799C8", "#D2D2D2", "#7B7B7B","#585757")
funcGA$Funding <- signif(funcGA$Funding, 5)
# hc <- funcGA %>%
#   hchart(
#     "pie", hcaes(x = Category, y = Funding),
#     name = "Funding ($)",
#     tooltip= list(formattable::currency(funcGA$Funding,digits=0L)))%>%
#     hc_colors(colors)%>%
#     hc_plotOptions(pie=list(
#       dataLabels = list(enabled = FALSE)
#       ))%>%
#     hc_size(height=400,width=400)%>%
#     hc_title(
#     text = "Georgia Funding by Category",
#     margin = 20,
#     align = "left"
#   )
# hc
```
</div>
<div class = "col-md-5">
```{r, echo=FALSE, fig.align='center'}
funcGA <- funcGA %>% add_row(Category = "Total", Funding=sum(funcGA$Funding))
funcGA$Funding <- signif(funcGA$Funding, 5)
funcGA$Funding <- currency(funcGA$Funding, digits = 0L)
funcGA%>% select(Category, Funding)%>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, html_font="Open Sans", font_size = 14)%>%
  add_header_above(c("Georgia Funding by Category"=2))%>%
  row_spec(1:16, color  = "#444444")%>%
  column_spec(1, "10cm")%>%
  column_spec(2, "3cm")
```
</div>
<h4>Spotlight on Projects</h4>
City of Atlanta: The Environmental Protection Agency committed $3.9 million to the City of Atlanta for brownfield remediation at five sites. The sites will be redeveloped or repurposed into affordable housing units, an environmental education center, parks, and mixed-use sites.

Solvay: The Department of Energy committed $178 million to Solvary to build a polyvinylidene fluoride (PVDF) facility in Augusta, Georgia. The facility is expected to supply over 5 million EV batteries per year at full capacity and create more than 100 highly skilled manufacturing jobs.

##### Kentucky
<div class = "row">
<div class = "col-md-7" style="padding-right:25px;">
```{r, echo=FALSE, fig.align='center'}

#function and award type data, filter to Kentucky
funcKY <-dplyr::filter(funData, recipient_state=="KY")%>%
  group_by(budget_subfunction) %>% dplyr::summarise(
  Funding = sum(transaction_obligated_amount)
  )%>% as.data.frame()

funcKY$Percent <- 100*(funcKY$Funding/sum(funcKY$Funding))
funcKY$Percent <- format(round(funcKY$Percent, 2), nsmall=2)
funcKY$Percent <- as.numeric(funcKY$Percent)

funcKY$zone.start <- with(funcKY, c(0, cumsum(Percent)[-length(Percent)]))
funcKY$zone.end <- with(funcKY, cumsum(Percent))
funcKY$label.point <- with(funcKY, (100-(zone.start + zone.end) / 2))

colnames(funcKY)[1] <- "Category"

pie <- ggplot(funcKY, aes(x="", y=Percent, fill=Category))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start=0)+
  scale_fill_manual(values=c("#FFA07A","#F08080", "#900C3F", "#C70039", "#D4442D","#FFF7B3","#154360","#00869F", "#6171AF","#DCB6D0","#C799C8","#D2D2D2","#7B7B7B","#585757")) +
  geom_text_repel(data = funcKY,
                   aes(y = label.point, label = ifelse(Percent>10,paste0(Percent, "%"),""), family="Open Sans"),
size = 4.5, color="#444444", nudge_x = 1, show.legend = FALSE) +
  ggtitle("Kentucky Funding by Category")+
  theme_void(base_family="Open Sans")+
  theme(legend.text=element_text(size=12, color="#444444"), 
       plot.title = element_text(color = "#444444"), 
       legend.title = element_text(color = "#444444"))
pie

# colors <- c("#FFA07A","#F08080", "#900C3F", "#C70039", "#D4442D","#00869F", "#6171AF","#DCB6D0","#C799C8","#7B7B7B","#585757")
funcKY$Funding <- signif(funcKY$Funding, 5)
# hc <- funcKY %>%
#   hchart(
#     "pie", hcaes(x = Category, y = Funding),
#     name = "Funding ($)",
#     tooltip= list(formattable::currency(funcKY$Funding,digits=0L)))%>%
#     hc_colors(colors)%>%
#     hc_plotOptions(pie=list(
#       dataLabels = list(enabled = FALSE)
#       ))%>%
#     hc_size(height=400,width=400)%>%
#     hc_title(
#     text = "Kentucky Funding by Category",
#     margin = 20,
#     align = "left"
#   )
# hc
```
</div>
<div class = "col-md-5">
```{r, echo=FALSE, fig.align='center'}
funcKY <- funcKY %>% add_row(Category = "Total", Funding=sum(funcKY$Funding))
funcKY$Funding <- signif(funcKY$Funding, 5)
funcKY$Funding <- currency(funcKY$Funding, digits = 0L)
funcKY%>% select(Category, Funding)%>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, html_font="Open Sans", font_size = 14)%>%
  add_header_above(c("Kentucky Funding by Category"=2))%>%
  row_spec(1:14, color  = "#444444")%>%
  column_spec(1, "10cm")%>%
  column_spec(2, "3cm")
```
</div>
<h4>Spotlight on Projects</h4>
Kentucky Energy and Environment Cabinet: The Department of Interior committed $74.3 million to Kentucky for mine reclamation.

Ascend Elements: The Department of Energy committed $316 million to Ascend Elements to build a manufacturing and EV batteries recycling facility. The facility will produce enough precursor and battery-ready cathode active materials for 250,000 EVs per year.

##### Louisiana
<div class = "row">
<div class = "col-md-7" style="padding-right:25px;">
```{r, echo=FALSE, fig.align='center'}

#function and award type data, filter to Louisiana
funcLA <-dplyr::filter(funData, recipient_state=="LA")%>%
  group_by(budget_subfunction) %>% dplyr::summarise(
  Funding = sum(transaction_obligated_amount)
  )%>% as.data.frame()
funcLA$budget_subfunction[7] <- "General property management"

funcLA$Percent <- 100*(funcLA$Funding/sum(funcLA$Funding))
funcLA$Percent <- format(round(funcLA$Percent, 2), nsmall=2)
funcLA$Percent <- as.numeric(funcLA$Percent)

funcLA$zone.start <- with(funcLA, c(0, cumsum(Percent)[-length(Percent)]))
funcLA$zone.end <- with(funcLA, cumsum(Percent))
funcLA$label.point <- with(funcLA, (100-(zone.start + zone.end) / 2))

colnames(funcLA)[1] <- "Category"

pie <- ggplot(funcLA, aes(x="", y=Percent, fill=Category))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start=0)+
  scale_fill_manual(values=c("#FFA07A","#F08080","#900C3F", "#C70039", "#D4442D","#FFF7B3","#AAC5E2","#154360","#00869F","#6171AF","#DCB6D0","#C799C8","#D2D2D2","#7B7B7B","#585757")) +
  geom_text_repel(data = funcLA,
                   aes(y = label.point, label = ifelse(Percent>10,paste0(Percent, "%"),""), family="Open Sans"),
size = 4.5, color="#444444", nudge_x = 1, show.legend = FALSE) +
  ggtitle("Louisiana Funding by Category")+
  theme_void(base_family= "Open Sans")+
  theme(legend.text=element_text(size=12, color="#444444"), 
       plot.title = element_text(color = "#444444"), 
       legend.title = element_text(color = "#444444"))
pie

# colors <- c("#FFA07A","#900C3F", "#C70039", "#D4442D","#FFF7B3","#AAC5E2","#00869F","#6171AF","#DCB6D0","#C799C8","#7B7B7B","#585757")
funcLA$Funding <- signif(funcLA$Funding, 5)
# hc <- funcLA %>%
#   hchart(
#     "pie", hcaes(x = Category, y = Funding),
#     name = "Funding ($)",
#     tooltip= list(formattable::currency(funcLA$Funding,digits=0L)))%>%
#     hc_colors(colors)%>%
#     hc_plotOptions(pie=list(
#       dataLabels = list(enabled = FALSE)
#       ))%>%
#     hc_size(height=400,width=400)%>%
#     hc_title(
#     text = "Louisiana Funding by Category",
#     margin = 20,
#     align = "left"
#   )
# hc
```
</div>
<div class = "col-md-5">
```{r, echo=FALSE, fig.align='center'}
funcLA <- funcLA %>% add_row(Category = "Total", Funding=sum(funcLA$Funding))
funcLA$Funding <- signif(funcLA$Funding, 5)
funcLA$Funding <- currency(funcLA$Funding, digits = 0L)
funcLA%>% select(Category, Funding)%>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, html_font="Open Sans", font_size = 14)%>%
  add_header_above(c("Louisiana Funding by Category"=2))%>%
  row_spec(1:15, color  = "#444444")%>%
  column_spec(1, "10cm")%>%
  column_spec(2, "3cm")
```
</div>
<h4>Spotlight on Projects</h4>
Jefferson Parish, Louisiana: The Department of Transportation committed $6.9 million to the Jefferson Parish, Louisiana, to purchase three diesel-electric buses and construct new administrative and maintenance buildings.

Louisiana Department of Natural Resources: The Department of Interior committed $25 million to the Louisiana DNR to plug and restore orphaned wells, implement methane monitoring protocols, and improve water quality monitoring.


##### Mississippi
<div class = "row">
<div class = "col-md-7" style="padding-right:25px;">
```{r, echo=FALSE, fig.align='center'}

#function and award type data, filter to Mississippi
funcMS <-dplyr::filter(funData, recipient_state=="MS")%>%
  group_by(budget_subfunction) %>% dplyr::summarise(
  Funding = sum(transaction_obligated_amount)
  )%>% as.data.frame()

funcMS$Percent <- 100*(funcMS$Funding/sum(funcMS$Funding))
funcMS$Percent <- format(round(funcMS$Percent, 2), nsmall=2)
funcMS$Percent <- as.numeric(funcMS$Percent)

funcMS$zone.start <- with(funcMS, c(0, cumsum(Percent)[-length(Percent)]))
funcMS$zone.end <- with(funcMS, cumsum(Percent))
funcMS$label.point <- with(funcMS, (100-(zone.start + zone.end) / 2))

colnames(funcMS)[1] <- "Category"

pie <- ggplot(funcMS, aes(x="", y=Percent, fill=Category))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start=0)+
  scale_fill_manual(values=c("#FFA07A","#F08080","#900C3F", "#C70039", "#D4442D","#FFF7B3","#00869F", "#6171AF","#DCB6D0","#C799C8","#D2D2D2","#7B7B7B","#585757")) +
  geom_text_repel(data = funcMS,
                   aes(y = label.point, label = ifelse(Percent>10,paste0(Percent, "%"),""),family="Open Sans"),
 size = 4.5, color="#444444", nudge_x = 1, show.legend = FALSE) +
  ggtitle("Mississippi Funding by Category")+
  theme_void(base_family="Open Sans")+
  theme(legend.text=element_text(size=12, color="#444444"), 
       plot.title = element_text(color = "#444444"), 
       legend.title = element_text(color = "#444444"))
pie

# colors <- c("#FFA07A","#900C3F", "#C70039", "#D4442D","#00869F", "#6171AF","#DCB6D0","#C799C8","#7B7B7B","#585757")
funcMS$Funding <- signif(funcMS$Funding, 5)
# hc <- funcMS %>%
#   hchart(
#     "pie", hcaes(x = Category, y = Funding),
#     name = "Funding ($)",
#     tooltip= list(formattable::currency(funcMS$Funding,digits=0L)))%>%
#     hc_colors(colors)%>%
#     hc_plotOptions(pie=list(
#       dataLabels = list(enabled = FALSE)
#       ))%>%
#     hc_size(height=400,width=400)%>%
#     hc_title(
#     text = "Mississippi Funding by Category",
#     margin = 20,
#     align = "left"
#   )
# hc
```
</div>
<div class = "col-md-5">
```{r, echo=FALSE, fig.align='center'}
funcMS <- funcMS %>% add_row(Category = "Total", Funding=sum(funcMS$Funding))
funcMS$Funding <- signif(funcMS$Funding, 5)
funcMS$Funding <- currency(funcMS$Funding, digits = 0L)
funcMS%>% select(Category, Funding)%>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, html_font="Open Sans", font_size = 14)%>%
  add_header_above(c("Mississippi Funding by Category"=2))%>%
  row_spec(1:13, color  = "#444444")%>%
  column_spec(1, "10cm")%>%
  column_spec(2, "3cm")
```
</div>
<h4>Spotlight on Projects</h4>
Syrah: The Department of Energy committed $220 million to expand Syrah's natural graphite active anode material (AAM) facility. This facility will be the first large-scale natural graphite AAM facility in the United States, used for EV and critical energy storage batteries.

Mississippi State Department of Health: The EPA committed $19.4 million to the Mississippi State Department of Health for improving public water systems, including fixing leaky or old pipes, improving the water supply, replacing or constructing finished water storage tanks, and more.

##### North Carolina
<div class = "row">
<div class = "col-md-7" style="padding-right:25px;">
```{r, echo=FALSE, fig.align='center'}

#function and award type data, filter to NC
funcNC <-dplyr::filter(funData, recipient_state=="NC")%>%
  group_by(budget_subfunction) %>% dplyr::summarise(
  Funding = sum(transaction_obligated_amount)
  )%>% as.data.frame()

funcNC$Percent <- 100*(funcNC$Funding/sum(funcNC$Funding))
funcNC$Percent <- format(round(funcNC$Percent, 2), nsmall=2)
funcNC$Percent <- as.numeric(funcNC$Percent)

funcNC$zone.start <- with(funcNC, c(0, cumsum(Percent)[-length(Percent)]))
funcNC$zone.end <- with(funcNC, cumsum(Percent))
funcNC$label.point <- with(funcNC, (100-(zone.start + zone.end) / 2))

colnames(funcNC)[1] <- "Category"

pie <- ggplot(funcNC, aes(x="", y=Percent, fill=Category))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start=0)+
  scale_fill_manual(values=c("#FFA07A","#F08080","#900C3F", "#C70039", "#D4442D","#FFF7B3","#52BE80","#75C7D3", "#00869F", "#6171AF","#DCB6D0","#C799C8", "#D2D2D2", "#7B7B7B","#585757")) +
  geom_text_repel(data = funcNC,
                   aes(y = label.point, label = ifelse(Percent>10,paste0(Percent, "%"),""),family="Open Sans"),
size = 4.5, color="#444444", nudge_x = 1, show.legend = FALSE) +
  ggtitle("North Carolina Funding by Category")+
  theme_void(base_family="Open Sans")+
  theme(legend.text=element_text(size=12, color="#444444"), 
       plot.title = element_text(color = "#444444"), 
       legend.title = element_text(color = "#444444"))
pie

# colors <- c("#FFA07A","#900C3F", "#C70039", "#D4442D","#52BE80","#75C7D3", "#00869F", "#6171AF","#DCB6D0","#C799C8", "#D2D2D2", "#7B7B7B","#585757")
funcNC$Funding <- signif(funcNC$Funding, 5)
# hc <- funcNC %>%
#   hchart(
#     "pie", hcaes(x = Category, y = Funding),
#     name = "Funding ($)",
#     tooltip= list(formattable::currency(funcNC$Funding,digits=0L)))%>%
#     hc_colors(colors)%>%
#     hc_plotOptions(pie=list(
#       dataLabels = list(enabled = FALSE)
#       ))%>%
#     hc_size(height=400,width=400)%>%
#     hc_title(
#     text = "North Carolina Funding by Category",
#     margin = 20,
#     align = "left"
#   )
# hc
```
</div>
<div class = "col-md-5">
```{r, echo=FALSE, fig.align='center'}
funcNC <- funcNC %>% add_row(Category = "Total", Funding=sum(funcNC$Funding))
funcNC$Funding <- signif(funcNC$Funding, 5)
funcNC$Funding <- currency(funcNC$Funding, digits = 0L)
funcNC%>% select(Category, Funding)%>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, html_font="Open Sans", font_size = 14)%>%
  add_header_above(c("North Carolina Funding by Category"=2))%>%
  row_spec(1:15, color  = "#444444")%>%
  column_spec(1, "10cm")%>%
  column_spec(2, "3cm")
```
</div>
<h4>Spotlight on Projects</h4>
Applied Materials: The Department of Energy committed $100 million to Applied Materials to build a pre-lithiation and lithium anode facility to support the EV battery supply chain. Applied Materials will build the facility in North Carolina and has not yet finalized an exact location.

Eastern Band of Cherokee Indians: The Department of Commerce committed $500,000 to the Eastern Band of Cherokee Indians for the initial phase of a broadband initiative, including rights-of-way, appraisals, project inspection fees, and project management.

##### South Carolina
<div class = "row">
<div class = "col-md-7" style="padding-right:25px;">
```{r, echo=FALSE, fig.align='center'}

#function and award type data, filter to SC
funcSC <-dplyr::filter(funData, recipient_state=="SC")%>%
  group_by(budget_subfunction) %>% dplyr::summarise(
  Funding = sum(transaction_obligated_amount)
  )%>% as.data.frame()

funcSC$Percent <- 100*(funcSC$Funding/sum(funcSC$Funding))
funcSC$Percent <- format(round(funcSC$Percent, 2), nsmall=2)
funcSC$Percent <- as.numeric(funcSC$Percent)

funcSC$zone.start <- with(funcSC, c(0, cumsum(Percent)[-length(Percent)]))
funcSC$zone.end <- with(funcSC, cumsum(Percent))
funcSC$label.point <- with(funcSC, (100-(zone.start + zone.end) / 2))

colnames(funcSC)[1] <- "Category"

pie <- ggplot(funcSC, aes(x="", y=Percent, fill=Category))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start=0)+
  scale_fill_manual(values=c("#FFA07A","#F08080", "#900C3F", "#C70039", "#D4442D","#FFF7B3","#154360","#00869F", "#6171AF","#DCB6D0","#C799C8", "#D2D2D2", "#7B7B7B","#585757")) +
  geom_text_repel(data = funcSC,
                   aes(y = label.point, label = ifelse(Percent>10,paste0(Percent, "%"),""), family="Open Sans"),
size = 4.5, color="#444444", nudge_x = 1, show.legend = FALSE) +
  ggtitle("South Carolina Funding by Category")+
  theme_void(base_family="Open Sans")+
  theme(legend.text=element_text(size=12, color="#444444"), 
       plot.title = element_text(color = "#444444"), 
       legend.title = element_text(color = "#444444"))
pie

# colors <- c("#FFA07A","#900C3F", "#C70039", "#D4442D","#52BE80","#75C7D3", "#00869F", "#6171AF","#DCB6D0","#C799C8", "#D2D2D2", "#7B7B7B","#585757")
funcSC$Funding <- signif(funcSC$Funding, 5)

# hc <- funcSC %>%
#   hchart(
#     "pie", hcaes(x = Category, y = Funding),
#     name = "Funding ($)",
#     tooltip= list(formattable::currency(funcSC$Funding,digits=0L)))%>%
#     hc_colors(colors)%>%
#     hc_plotOptions(pie=list(
#       dataLabels = list(enabled = FALSE)
#       ))%>%
#     hc_size(height=400,width=400)%>%
#     hc_title(
#     text = "South Carolina Funding by Category",
#     margin = 20,
#     align = "left"
#   )
# hc
```
</div>
<div class = "col-md-5">
```{r, echo=FALSE, fig.align='center'}
funcSC <- funcSC %>% add_row(Category = "Total", Funding=sum(funcSC$Funding))
funcSC$Funding <- signif(funcSC$Funding, 5)
funcSC$Funding <- currency(funcSC$Funding, digits = 0L)
funcSC%>% select(Category, Funding)%>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, html_font="Open Sans", font_size = 14)%>%
  add_header_above(c("South Carolina Funding by Category"=2))%>%
  row_spec(1:14, color  = "#444444")%>%
  column_spec(1, "10cm")%>%
  column_spec(2, "3cm")
```
</div>

<h4>Spotlight on Projects</h4>
City of Clemson, SC: The Department of Commerce committed $3.9 million to the City of Clemson, South Carolina, for zero-emission battery electric buses to replace diesel buses that have exceeded their useful life.

##### Tennessee
<div class = "row">
<div class = "col-md-7" style="padding-right:25px;">
```{r, echo=FALSE, fig.align='center'}

#function and award type data, filter to Tennessee
funcTN <-dplyr::filter(funData, recipient_state=="TN")%>%
  group_by(budget_subfunction) %>% dplyr::summarise(
  Funding = sum(transaction_obligated_amount)
  )%>% as.data.frame()
funcTN$budget_subfunction[7] <- "General property management"

funcTN$Percent <- 100*(funcTN$Funding/sum(funcTN$Funding))
funcTN$Percent <- format(round(funcTN$Percent, 2), nsmall=2)
funcTN$Percent <- as.numeric(funcTN$Percent)

funcTN$zone.start <- with(funcTN, c(0, cumsum(Percent)[-length(Percent)]))
funcTN$zone.end <- with(funcTN, cumsum(Percent))
funcTN$label.point <- with(funcTN, (100-(zone.start + zone.end) / 2))

colnames(funcTN)[1] <- "Category"

pie <- ggplot(funcTN, aes(x="", y=Percent, fill=Category))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start=0)+
  scale_fill_manual(values=c("#FFA07A","#F08080", "#900C3F", "#C70039", "#D4442D","#FFF7B3","#AAC5E2","#154360","#00869F","#6171AF","#DCB6D0","#C799C8", "#D2D2D2", "#7B7B7B","#585757")) +
  geom_text_repel(data = funcTN,
                   aes(y = label.point, label = ifelse(Percent>10,paste0(Percent, "%"),""),family="Open Sans"),
size = 4.5, color="#444444", nudge_x = 1, show.legend = FALSE) +
  ggtitle("Tennessee Funding by Category")+
  theme_void(base_family="Open Sans")+
  theme(legend.text=element_text(size=12, color="#444444"), 
       plot.title = element_text(color = "#444444"), 
       legend.title = element_text(color = "#444444"))
pie

# colors <- c("#FFA07A","#F08080", "#900C3F", "#C70039", "#D4442D","#FFF7B3","#AAC5E2","#00869F","#6171AF","#DCB6D0","#C799C8", "#D2D2D2", "#7B7B7B","#585757")
funcTN$Funding <- signif(funcTN$Funding, 5)

# hc <- funcTN %>%
#   hchart(
#     "pie", hcaes(x = Category, y = Funding),
#     name = "Funding ($)",
#     tooltip= list(formattable::currency(funcTN$Funding,digits=0L)))%>%
#     hc_colors(colors)%>%
#     hc_plotOptions(pie=list(
#       dataLabels = list(enabled = FALSE)
#       ))%>%
#     hc_size(height=400,width=400)%>%
#     hc_title(
#     text = "Tennessee Funding by Category",
#     margin = 20,
#     align = "left"
#   )
# hc
```
</div>
<div class = "col-md-5">
```{r, echo=FALSE, fig.align='center'}
funcTN <- funcTN %>% add_row(Category = "Total", Funding=sum(funcTN$Funding))
funcTN$Funding <- signif(funcTN$Funding, 5)
funcTN$Funding <- currency(funcTN$Funding, digits = 0L)
funcTN%>% select(Category, Funding)%>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, html_font="Open Sans", font_size = 14)%>%
  add_header_above(c("Tennessee Funding by Category"=2))%>%
  row_spec(1:16, color  = "#444444")%>%
  column_spec(1, "10cm")%>%
  column_spec(2, "3cm")
```
</div>
<h4>Spotlight on Projects</h4>
Economic Development Growth Engine for Memphis and Shelby County: The Environmental Protection Agency committed $1 million to finance a revolving loan fund for brownfield cleanup. The grant will specifically target four sites, including a historic school for African Americans and a site at which the State of Tennessee stored contaminated soil in the 1960s.

Piedmont Lithium: The Department of Energy committed $141.7 million to Piedmont Lithium to build a lithium hydroxide facility in Etowah, Tennessee that will strengthen the domestic EV battery supply chain. The facility is expected to produce 30,000 metric tons of lithium hydroxide per year, doubling the current U.S. production.

##### Virginia
<div class = "row">
<div class = "col-md-7" style="padding-right:25px;">
```{r, echo=FALSE, fig.align='center'}

#function and award type data, filter to Virginia
funcVA <-dplyr::filter(funData, recipient_state=="VA")%>%
  group_by(budget_subfunction) %>% dplyr::summarise(
  Funding = sum(transaction_obligated_amount)
  )%>% as.data.frame()
funcVA$budget_subfunction[10] <- "General Property Management"

funcVA$Percent <- 100*(funcVA$Funding/sum(funcVA$Funding))
funcVA$Percent <- format(round(funcVA$Percent, 2), nsmall=2)
funcVA$Percent <- as.numeric(funcVA$Percent)

funcVA$zone.start <- with(funcVA, c(0, cumsum(Percent)[-length(Percent)]))
funcVA$zone.end <- with(funcVA, cumsum(Percent))
funcVA$label.point <- with(funcVA, (100-(zone.start + zone.end) / 2))

colnames(funcVA)[1] <- "Category"

pie <- ggplot(funcVA, aes(x="", y=Percent, fill=Category))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start=0)+
  scale_fill_manual(values=c("#FFA07A","#F08080","#900C3F", "#C70039", "#D4442D", "#FCB616","#FFF7B3","#8FED94", "#52BE80", "#AAC5E2", "#75C7D3","#154360","#00869F","#61195E", "#6171AF","#DCB6D0","#C799C8", "#D2D2D2", "#7B7B7B","#585757")) +
  geom_text_repel(data = funcVA,
                   aes(y = label.point, label = ifelse(Percent>10,paste0(Percent, "%"),""),family="Open Sans"),
color="#444444", size = 4.5, nudge_x = 1, show.legend = FALSE) +
  ggtitle("Virginia Funding by Category")+
  theme_void(base_family="Open Sans")+
  theme(legend.text=element_text(size=12, color="#444444"), 
       plot.title = element_text(color = "#444444"), 
       legend.title = element_text(color = "#444444"))
pie

# colors <- c("#FFA07A","#900C3F", "#C70039", "#D4442D", "#FCB616","#FFF7B3","#8FED94", "#52BE80", "#AAC5E2", "#75C7D3", "#00869F", "#6171AF","#DCB6D0","#C799C8", "#D2D2D2", "#7B7B7B","#585757")
funcVA$Funding <- signif(funcVA$Funding, 5)

# hc <- funcVA %>%
#   hchart(
#     "pie", hcaes(x = Category, y = Funding),
#     name = "Funding ($)",
#     tooltip= list(formattable::currency(funcVA$Funding,digits=0L)))%>%
#     hc_colors(colors)%>%
#     hc_plotOptions(pie=list(
#       dataLabels = list(enabled = FALSE)
#       ))%>%
#     hc_size(height=400,width=400)%>%
#     hc_title(
#     text = "Virginia Funding by Category",
#     margin = 20,
#     align = "left"
#   )
# hc
```
</div>
<div class = "col-md-5">
```{r, echo=FALSE, fig.align='center'}
funcVA <- funcVA %>% add_row(Category = "Total", Funding=sum(funcVA$Funding))
funcVA$Funding <- signif(funcVA$Funding, 5)
funcVA$Funding <- currency(funcVA$Funding, digits = 0L)
funcVA%>% select(Category, Funding)%>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, html_font="Open Sans", font_size = 14)%>%
  add_header_above(c("Virginia Funding by Category"=2))%>%
  row_spec(1:20, color  = "#444444")%>%
  column_spec(1, "10cm")%>%
  column_spec(2, "3cm")
```
</div>

<h4>Spotlight on Projects</h4>
National Association of State Energy Officials: The Department of Energy awarded $1.5 million to NASEO for their work building a national electric vehicle infrastructure network.

### Funding By Category

``` {r echo=FALSE}
funcSE <- funData %>% dplyr::filter(recipient_state %in% targetM)%>% 
  group_by(budget_subfunction) %>% dplyr::summarise(
  Funding = sum(transaction_obligated_amount)
  )%>% as.data.frame()

funcSE$Percent <- 100*(funcSE$Funding/sum(funcSE$Funding))
funcSE$Percent <- format(round(funcSE$Percent, 2), nsmall=2)
funcSE$Percent <- as.numeric(funcSE$Percent)

funcSE$zone.start <- with(funcSE, c(0, cumsum(Percent)[-length(Percent)]))
funcSE$zone.end <- with(funcSE, cumsum(Percent))
funcSE$label.point <- with(funcSE, (100-(zone.start + zone.end) / 2))

colnames(funcSE)[1] <- "Category"

pie <- ggplot(funcSE, aes(x="", y=Percent, fill=Category))+
  geom_bar(width = 1, stat = "identity", show.legend = FALSE)+
  coord_polar("y", start=0)+
  scale_fill_manual(values=c("#FFA07A","#F08080", "#900C3F", "#C70039", "#D4442D", "#FCB616","#FFF7B3","#8FED94", "#52BE80", "#AAC5E2", "#75C7D3", "#154360","#00869F", "#61195E", "#6171AF","#DCB6D0","#C799C8", "#D2D2D2", "#7B7B7B","#585757", "#000000")) +
  geom_text_repel(data = funcSE,
                   aes(y = label.point, label = ifelse(Percent>5 | Category == 'Energy conservation' ,paste0(Percent, "%"),""), family="Open Sans"),
size = 4.5, color= "#444444", nudge_x = 1, show.legend = FALSE) +
  ggtitle("Southeast Funding by Category")+
  theme(plot.title = element_text(size=12))+
  theme_void(base_family= "Open Sans")+
  theme(legend.key.height = unit(.3,'cm'),
        legend.key.width = unit(.3, 'cm'),
        legend.text=element_text(size=10, color="#444444"),
       plot.title = element_text(color = "#444444"),
       legend.title = element_text(color = "#444444"))
pie

# ggsave("C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/Categories_02_2024.png", width = 6,   height = 4.25, dpi=1100)
```

``` {r echo=FALSE, out.width="80%"}
funcSE$Funding <- signif(funcSE$Funding, 5)
funcSE$Funding <- formattable::currency(funcSE$Funding, digits = 0L)
funcSE%>% select(Category, Funding)%>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width=F, font_size=14, html_font="Open Sans")%>%
  add_header_above(c("Southeast Funding by Category"=2))%>%
  row_spec(1:21, color  = "#444444")%>%
  column_spec(1, "10cm")%>%
  column_spec(2,"3cm")
```

### Funding by Award Type
<div class = "row">
<div class = "col-md-7" style="padding-right:25px;">
``` {r echo=FALSE}
fundByType <-group_by(funData,award_type) %>% dplyr::summarise(
  Funding = sum(transaction_obligated_amount)
  )%>% as.data.frame()

fundByType$Percent <- 100*(fundByType$Funding/sum(fundByType$Funding))
fundByType$Percent <- format(round(fundByType$Percent, 2), nsmall=2)
fundByType$Percent <- as.numeric(fundByType$Percent)

fundByType$zone.start <- with(fundByType, c(0, cumsum(Percent)[-length(Percent)]))
fundByType$zone.end <- with(fundByType, cumsum(Percent))
fundByType$label.point <- with(fundByType, (100-(zone.start + zone.end) / 2))

fundByType$award_type[7] <- "Direct Payment Specified Use"
fundByType$award_type[11] <- "Other Financial Assistance"
colnames(fundByType)[1] <- "Type"
fundByType$Type <- str_to_title(fundByType$Type)
fundByType$Type[2] <- "BPA Call"
fundByType$Type[1] <- "Block Grant"
fundByType$Type[3] <- "Cooperative Agreement"
fundByType$Type[6] <- "Direct Loan"
fundByType$Type[8] <- "Formula Grant"
fundByType$Type[12] <- "Project Grant"

pie2 <- ggplot(fundByType, aes(x="", y=Percent, fill=Type))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start=0)+
  scale_fill_manual(values=c("#900C3F", "#C70039", "#D4442D", "#FCB616", "#52BE80", "#AAC5E2", "#75C7D3", "#00869F", "#6171AF","#DCB6D0","#C799C8", "#D2D2D2", "#7B7B7B","#585757")) +
  geom_text_repel(data = fundByType,
                   aes(y = label.point, label = ifelse(Percent>5,paste0(Percent, "%"),""),family="Open Sans"),
size = 4.5, color="#444444", nudge_x = 1, show.legend = FALSE, max.overlaps =20) +
  ggtitle("Southeast Funding by Award Type")+
  theme_void(base_family= "Open Sans")+
  theme(plot.title = element_text(size=12, color = "#444444"),
        legend.text=element_text(size=12, color="#444444"), 
       legend.title = element_text(color = "#444444"))
  
pie2

# ggsave("C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/award_type_02_2024.png", width = 6,   height = 4, dpi=1100)
```
</div>

<div class = "col-md-5">
``` {r echo=FALSE, out.width="80%"}
fundByType$Funding <- signif(fundByType$Funding, 5)
fundByType$Funding <- formattable::currency(fundByType$Funding, digits = 0L)
fundByType%>% select(Type, Funding)%>% kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width=F, font_size=14, html_font="Open Sans")%>%
  add_header_above(c("Southeast Funding by Type"=2))%>%
  row_spec(1:13, color  = "#444444")%>%
  column_spec(1, "10cm")%>%
  column_spec(2,"3cm")
```
</div>
### Energy Funding 
<div class = "row">
<div class = "col-md-6" style="padding-right:20px;">
``` {r echo=FALSE, out.width="80%"}
###Weatherization Assistance Program Funding
# WAPdata <- read.csv("C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/Southeast_DOE_funding_BIL/Southeast_DOE_BIL_PrimeAwards.csv")%>%select(obligated_amount_from_IIJA_supplemental, program_activities_funding_this_award, recipient_name, cfda_numbers_and_titles, recipient_state_name)%>%filter(cfda_numbers_and_titles == "81.042: WEATHERIZATION ASSISTANCE FOR LOW-INCOME PERSONS")
WAPdata <- funData %>%select(transaction_obligated_amount, program_activity_name, recipient_name, cfda_number, cfda_title, recipient_state)%>%filter(cfda_number == 81.042)%>%
  filter(recipient_state %in% targetM)%>%
  group_by(recipient_name)%>%
  dplyr::summarise(Funding = sum(transaction_obligated_amount))
  
colnames(WAPdata)[2] <- "Funding"
colnames(WAPdata)[1] <- "Recipient"
WAPdata$Recipient <- paste(str_to_title(WAPdata$Recipient))
WAPdata$Funding <- signif(WAPdata$Funding, 5)
WAPdata$Funding <- currency(WAPdata$Funding, digits = 0L)
WAPdata <- WAPdata[order(WAPdata$Funding,decreasing=TRUE),]
WAPdata$Recipient[7] <- "Alabama Department of Economic and Community Affairs"
WAPdata$Recipient[8] <- "South Carolina Office of the State Treasurer"
WAPdata$Recipient[10] <- "Mississippi Department of Human Services"
WAPdata$Recipient[11] <- "Arkansas Division of Environmental Quality"
WAPdata$Recipient[5] <- "Virginia Department of Housing and Community Development"

WAPtable<- WAPdata%>% select(Recipient, Funding)%>% kbl(row.names=FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, html_font="Open Sans", font_size = 14)%>%  
  add_header_above(c("Weatherization Assistance Program Funding"=2))%>%
  row_spec(1:11, color  = "#444444")
  # column_spec(1, "12cm")%>%
  # column_spec(2, "3cm")
WAPtable
# save_kable(WAPtable,"C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/WAPtable.png")
WAPtotal <- sum(WAPdata$Funding)
```
</div>

<div class = "col-md-6">
```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="80%"}
###State Energy Office Funding
SEOdata <- funData%>%select(transaction_obligated_amount, program_activity_name, recipient_name, cfda_number, recipient_state)%>%filter(cfda_number == 81.041)%>%
  filter(recipient_state %in% targetM)%>%
  group_by(recipient_name)%>%
  dplyr::summarise(Funding = sum(transaction_obligated_amount))

colnames(SEOdata)[2] <- "Funding"
colnames(SEOdata)[1] <- "Recipient"
SEOdata$Recipient <- paste(str_to_title(SEOdata$Recipient))
SEOdata$Funding <- signif(SEOdata$Funding, 5)
SEOdata$Funding <- currency(SEOdata$Funding, digits = 0L)
SEOdata <- SEOdata[order(SEOdata$Funding,decreasing=TRUE),]
SEOdata$Recipient[7] <- "Alabama Department of Economic and Community Affairs"
SEOdata$Recipient[8] <- "Kentucky Energy and Environment Cabinet"
SEOdata$Recipient[11] <- "Arkansas Division of Environmental Quality"
SEOdata$Recipient[3] <- "Louisiana Department of Natural Resources"
SEOtable<-SEOdata%>% select(Recipient, Funding)%>% kbl(row.names=FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), html_font="Open Sans", font_size = 14, full_width = F)%>%
  add_header_above(c("State Energy Program Funding"=2))%>%
  row_spec(1:10, color  = "#444444")
  # column_spec(1, "12cm")%>%
  # column_spec(2, "3cm")
SEOtable
# save_kable(SEOtable,"C:/Users/GraceParker/Downloads/2023_FederalFundingTracker/SEOtable.png")
SEOtotal <- sum(SEOdata$Funding)

```
</div>
